Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-02-17 tex/nusselt_paper.tex
fixes ascl for dedalus (ben/geoff switch)
fixes the definition of Nu

The efficiency of convection is quantified by the Nusselt number.  
Nu is well-defined in RB convection
as the total flux normalized by the steady-state conductive flux 
\cite{johnston&doering2009, otero&all2002}.
In stratified convection Nu is more difficult to define, but one of the earliest definitions used
was \cite{graham1975,hurlburt&all1984}
\begin{equation}
\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the 
z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ 
is the adiabatic conductive flux and
$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
for an ideal gas in hydrostatic equilibrium.
The conductive flux of a linear profile connecting the upper
and lower plates
is $F_{\text{ref}} \equiv \Delta T / L_z$, 
where $\Delta T \equiv T(L_z) - T(0)$.  $F_{\text{ref}}$ is constant for 
the choice of fixed-temperature boundaries.

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

>>>>

The efficiency of convection is quantified by the Nusselt number.  
Nu is well-defined in RB convection
as the total flux normalized by the steady-state conductive flux 
\cite{johnston&doering2009, otero&all2002}.
In stratified convection Nu is more difficult to define, and we use
a modified version of a traditional stratified Nusselt number \cite{graham1975,hurlburt&all1984},
\begin{equation}
\text{Nu} \equiv \frac{\langle F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}\rangle}
{\langle F_{\text{cond, z}} - F_{\text{A}}\rangle} 
= 1 + \frac{\langle F_{\text{conv, z}}\rangle}{\langle F_{\text{cond, z}} - F_{\text{A}} \rangle}
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the 
z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
respectively and $\langle \rangle$ implies a volume average.  
$F_{\text{A}} \equiv -\langle\kappa\rangle \partial_z T_{\text{ad}}$ 
is the adiabatic conductive flux and
$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
for an ideal gas in hydrostatic equilibrium.  Here we specify
$\langle \kappa \rangle = \langle (\rho_{1}/\rho_{0})\kappa_0 \rangle$.
At large values of $\epsilon$, $\kappa$ evolves significantly as the
density profile evolves.  At low $\epsilon$, $\langle\kappa\rangle \approx \kappa_0$.

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
We thank Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi for many useful discussions.
